
\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{from \lstinline!stdin!}

Building an image on the fly, w/o using a static file

\begin{lstlisting}
touch myfile.sh
chmod +x myfile.sh
docker build -t foo . -f-<<EOF
FROM ubuntu:18.04
RUN echo "hello world"
COPY myfile.sh /opt/
EOF
\end{lstlisting}
\end{frame}


\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{with a remote context}

\begin{lstlisting}
docker build -t foo \
       https://github.com/thajeztah/pgadmin4-docker.git \
	   -f-<<EOF
	   FROM ubuntu:18.04
	   WORKDIR /usr/local/lib/python2.7/site-packages
	   COPY LICENSE pgadmin4/
	   COPY config_distro.py pgadmin4/
	   EOF
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{ignore files}

Unwanted files can be excluded from the context, by convention
a \lstinline!.dockerignore! file is required and using regular expression
is possible to exclude files.
\end{frame}

\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{ignore files}

\begin{itemize}
\item \lstinline!#!: defines a comment
\item \lstinline!*/temp*! Exclude files and directories whose names start with temp in any immediate subdirectory of the root.For example, the plain file \lstinline!/somedir/temporary.txt! is excluded, as is the directory \lstinline!/somedir/temp!.
\item \lstinline!|*/*/temp*! Exclude files and directories starting with temp from any sub-directory that is two levels below the root. For example, \lstinline!/somedir/subdir/temporary.txt! is excluded.
\item \lstinline!temp?! Exclude files and directories in the root directory whose names are a one-character extension of temp. For example, \lstinline!/tempa! and \lstinline!/tempb! are excluded.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{make it human readable}

When possible sorting multi-line arguments is recommended

\begin{lstlisting}
RUN apt-get update &&\
    apt-get install -y \
	    bzr \
		csv \
		git \
		mercurial \
		subversion \
		texlive
\end{lstlisting}
\end{frame}


\begin{frame}[fragile]
\frametitle{Dockerfile}
\framesubtitle{quick tips}

\begin{itemize}
\item Annotate the image with \lstinline!LABEL!
\item Use \lstinline!ENV! for keeping track of versions
\item \lstinline!COPY! is more transparent than \lstinline!ADD!
\item Use \lstinline!wget! or \lstinline!curl! for downloading from the web
\item The web does not guarantee URLs forever
  \begin{itemize}
  \item Consider to host a web/fileserver for \textit{very important} data or software
  \item Licensing can be an issue, some software can not be distributed freely
  \end{itemize}
\item Use \lstinline!WORKDIR! when possible
\item Image as executable ? \lstinline!ENTRYPOINT! is the way to go
  \begin{itemize}
  \item \lstinline!CMD! is used for default parameters \lstinline!--help!
  \end{itemize}
\item A regular user with \lstinline!root! privileges is worst than evil
  \begin{itemize}
  \item This applies only if it is your infrastructure \lstinline!:)!
  \item In most scientific infrastructures Docker is forbidden or masked by some wrapper
  \end{itemize}
\end{itemize}
\end{frame}
 
